SDG contributions

### 2023-09-06 article/article.qmd
remove 2019 altogether and add overall growth stats
reason for removing 2019: there was a substantial drop in publications in MAG in 2019 to the year before (-13%), which means the sample is not complete there. Calculating growth rates would thus be incorrect

# remove 2020 altogether
papers <- papers %>% 
  filter(year < 2020)
```

@@

TODO: make a better figure/table to view the growth rate

>>>>

# remove 2019-2020 altogether. my MAG copy was still incomplete for 2019
papers <- papers %>% 
  filter(year < 2019)
```

# Sample size
```{r}
# total sample size
papers %>% 
  sdf_nrow()
```

```{r}
# per SDG
papers %>% 
  count(SDG_label)
```

```{r}
papers %>% 
  group_by(year) %>% 
  filter(year %in% c(2006, 2018)) %>% 
  count(SDG_label) %>% 
  arrange(SDG_label, year)
```

@@

```{r growth-rates}
growth_rate_data <- merged_count %>% 
  arrange(SDG_label, year) %>% 
  group_by(SDG_label) %>% 
  mutate(prop_change = prop / lag(prop),
         prop_change = replace_na(prop_change, 1),
         prop_change = prop_change - 1)

growth_rate_data %>% 
  ggplot(aes(as_year(year), prop_change, colour = fix_sdg(SDG_label))) +
  geom_line() +
  geom_point() +
  colorspace::scale_color_discrete_qualitative() +
  scale_y_continuous(labels = scales::percent) +
  labs(x = NULL, y = "Yearly growth rate relative to total papers in MAG",
       colour = NULL,
       title = "Development of SDG areas over time") +
  theme(legend.position = "top")
```

```{r}
growth_rate_data %>% 
  filter(year %in% c(2006, 2018)) %>% 
  summarise(overall_growth_factor = {overall_n / lag(overall_n)}[2],
            individual_growth_factor = {n / lag(n)}[2],
            individual_growth_rate = individual_growth_factor^(1/(2018-2006)) - 1,
            overall_growth_rate = overall_growth_factor^(1/(2018-2006)) - 1) %>% 
  knitr::kable()

```

```{r}
spark_disconnect(sc)
```
